%-------------------------
% Resume in Latex
% Author : Jake Gutierrez (modified by Hadi Khan)
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.9in}
\addtolength{\textheight}{1.6in}
\setlength{\footskip}{4pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section format
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-3pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-4pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \small\textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-9pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------

\begin{document}

%----------HEADING----------
\begin{center}
\textbf{\Huge \scshape Hadi Khan} \\ \vspace{1pt}
\small +923156233633 $|$
\href{mailto:hello@mhadi.dev}{\underline{hello@mhadi.dev}} $|$
\href{https://www.linkedin.com/in/okhadi/}{\underline{linkedin.com/in/okHadi}} $|$
\href{https://www.mhadi.dev}{\underline{www.mhadi.dev}} $|$
\href{https://github.com/okHadi}{\underline{github.com/okHadi}}
\end{center}

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item \small{
\textbf{Languages}{: Python, TypeScript/JavaScript, Bash} \\
\textbf{Frameworks \& Libraries}{: ExpressJS, Flask, React, Selenium} \\
\textbf{Infra \& DevOps}{: AWS, Cloudflare, Docker, Terraform, Ansible, Vagrant, GitHub Actions, Datadog} \\
\textbf{Tools}{: Git, Postman}
}
\end{itemize}\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{Experience}

\resumeSubHeadingListStart

\resumeSubheading
{Assc. Product Manager (AI First)}{December 2025 -- Present}
{Imagine.art / Vyro.ai}{Islamabad, On Site}
\resumeItemListStart
\resumeItem{Led OmniAgent end-to-end as the new AI core of ChatlyAI, scaling from 0 to 5,000 DAUs and 15,000+ organic generations; owned execution from architecture to growth and contributed production PRs alongside the engineering team.}
\resumeItem{Independently built and launched Chatly's AI Chrome extension in 2 weeks using Claude, acquiring 2,000+ organic users post-launch with zero paid acquisition.}
\resumeItem{Owned the AI Slides feature end-to-end within 1 month: researched generation libraries, built a proof of concept, and architected the end-to-end pipeline from prompt to rendered slide output, reaching 10,000+ users.}
\resumeItem{Contributed to scaling the broader product from 200K to 1.2M+ MAUs (6x) and 10M+ sign-ups through feature prioritization, growth experiments, and cross-functional execution.}
\resumeItem{Supported revenue growth into the \$6.5M range through pricing experiments, funnel optimization, and Stripe billing.}
\resumeItem{Helped scale the product org from 5 to 35+ members while leading a cross-functional team of 10 engineers; built internal automation tools to reduce manual effort and improve delivery velocity.}
\resumeItem{Improved AI image generation quality ratings by 50\% through structured prompt engineering, model parameter tuning, and iterative testing across generation configurations.}
\resumeItem{Automated internal workflows (vendor invoicing, template updates, review tracking) via serverless functions, cutting hours-long processes to minutes and freeing engineering capacity for product work.}
\resumeItemListEnd

\resumeSubheading
{Co-Founder \& CTO}{Mar 2024 -- Present}
{Parhlai}{Islamabad / Remote}
\resumeItemListStart
\resumeItem{Founded and scaled an ed-tech platform to 4,000+ MAU, securing ~1M PKR in funding and generating 100K+ PKR in organic revenue; led a team of 4 engineers and won multiple hackathons, competitions, and grants.}
\resumeItem{Led product strategy and roadmap execution while championing an AI-first engineering culture to accelerate delivery.}
\resumeItem{Executed GTM via Reddit and referral programs and ranked key features at \#3 in search within 2 weeks using Ahrefs and SEO, driving acquisition with zero paid ads.}
\resumeItem{Implemented PostHog analytics to track user journeys, inform feature prioritization, and optimize retention.}
\resumeItem{Architected the full backend on serverless AWS (Lambda, CloudFront, S3) and Cloudflare (Workers, Durable Objects, KV), using Terraform for multi-environment deployments with infrastructure cost under 1\% of total spend.}
\resumeItem{Built an end-to-end MCQ generation pipeline (EasyOCR + YOLOv12 ingestion, Pinecone embeddings, Groq/Gemini generation) with a multi-agent validation system and DPP diversity sampling across 4 exam configurations.}
\resumeItem{Built an in-product chatbot on Cloudflare Workers, Groq (BYOK), Durable Objects, and KV for low-latency inference.}
\resumeItemListEnd


\resumeSubheading
{Backend and DevOps Engineer}{June 2021 -- December 2025}
{Syslify}{UK, Remote}
\resumeItemListStart
\resumeItem{Developed and deployed Dockerized Flask and TypeScript/Express apps across serverless (AWS Lambda) and managed (ECS Fargate, EC2) infrastructure, including MongoDB-backed backends for two e-commerce platforms.}
\resumeItem{Migrated CodeCommit, CodePipeline, and manual infrastructure to GitHub + Terraform IaC for multi-million-dollar startup clients, managing AWS, GCP, Cloudflare, and GitHub resources.}
\resumeItem{Built CI/CD pipelines on GitHub Actions and GitLab CI with Docker layer caching; provisioned self-hosted AWS Fargate runners, cutting costs ~90\%; automated on-demand ops (DB changes, WAF updates, state-lock removal).}
\resumeItem{Implemented blue/green deployments on ECS Fargate via CloudFormation, CodePipeline, and CodeDeploy, with a hotfix path for rapid production fixes.}
\resumeItem{Hardened access controls: SSO (Microsoft Entra ID), RBAC, GitHub Environments for secret scoping, temporary pipeline credentials, and Firebase Auth with custom admin roles.}
\resumeItem{Built observability stack with Bash/Python monitoring scripts, Slack/PagerDuty alerting, and Datadog agents deployed on EC2 and ECS Fargate for ElastiCache and service-level monitoring, improving incident detection by 50\%.}
\resumeItem{Configured CloudFront + AWS WAF to secure development endpoints; automated WAF access list updates and DNS management via Terraform and GitHub Actions.}
\resumeItem{Built disaster recovery with multi-region RDS snapshot replication and Cognito user pool backups.}
\resumeItem{Deployed static React sites via CloudFront + S3 and Cloudflare Pages; raised AWS Security Hub from ~60\% to ~80\% and cut infra costs ~70\% via EC2 rightsizing.}
\resumeItem{Managed and tuned OpenSearch clusters for production search workloads.}
\resumeItemListEnd

\resumeSubheading
{Associate Software Engineer}{Nov 2023 -- Sept 2024}
{Vfairs}{Lahore, Remote}
\resumeItemListStart
\resumeItem{Configured and executed load tests simulating up to 10,000 concurrent users to ensure system stability.}
\resumeItem{Developed and optimized 40+ job scrapers, increasing data acquisition by 50\%.}
\resumeItem{Designed and provisioned ephemeral QA environments on AWS ECS triggered by pull requests, enabling parallel testing across a team of 50+ developers.}
\resumeItemListEnd


\resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{National University of Science and Technology}{Islamabad, Pakistan}
{Bachelor of Science in Computer Science}{}
\resumeSubHeadingListEnd

\end{document}
