%-------------------------
% Resume in Latex
% Author : Jake Gutierrez (modified by Hadi Khan)
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.9in}
\addtolength{\textheight}{1.6in}
\setlength{\footskip}{4pt}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section format
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-3pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-4pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \small\textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-9pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------

\begin{document}

%----------HEADING----------
\begin{center}
\textbf{\Huge \scshape Hadi Khan} \\ \vspace{1pt}
\small +923156233633 $|$ 
\href{mailto:hello@mhadi.dev}{\underline{hello@mhadi.dev}} $|$
\href{https://www.linkedin.com/in/okhadi/}{\underline{linkedin.com/in/okHadi}} $|$
\href{https://www.mhadi.dev}{\underline{www.mhadi.dev}} $|$
\href{https://github.com/okHadi}{\underline{github.com/okHadi}}
\end{center}

%-----------SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\item \small{
\textbf{Languages}{: Python, TypeScript/Javascript, Bash} \\
\textbf{Product \& AI}{: PostHog, Ahrefs, SEO, GTM Strategy, User Analytics, Mixpanel} \\
\textbf{Libraries \& Tools}{: ExpressJS, Flask, React, Selenium, Postman, Git, Jira/Confluence/Linear} \\
\textbf{DevOps \& IaC}{: GitHub Actions, Datadog, AWS, Cloudflare, Docker, Terraform, Ansible, Vagrant}
}
\end{itemize}\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{Experience}

\resumeSubHeadingListStart

\resumeSubheading
{AI Product Manager}{December 2025 -- Present}
{Chatly / Vyro.ai}{Islamabad, On Site}
\resumeItemListStart
\resumeItem{Independently built and launched Chatly's AI Chrome extension in 2 weeks using Claude, acquiring 1,200+ organic users immediately post-launch.}
\resumeItem{Owned the product lifecycle for the "AI Slides" feature, from ideation to launch, driving 1,000+ users immediately post-launch through rapid iteration and user-focused design.}
\resumeItem{Improved AI Image Generation ratings by 50\% through prompt and UX iteration.}
\resumeItem{Automated internal workflows like invoicing, template updates, and review tracking to improve team velocity.}
\resumeItemListEnd

\resumeSubheading
{Co-Founder \& CTO}{Mar 2024 -- Present}
{Parhlai}{Islamabad / Remote}
\resumeItemListStart
\resumeItem{Founded and scaled an ed-tech platform, securing ~1M PKR in funding and generating 100K+ PKR in organic revenue.}
\resumeItem{Led product strategy and roadmap execution, aligning engineering efforts with growth and user engagement goals.}
\resumeItem{Championed an AI-first engineering culture, leveraging AI tools to accelerate development with a lean team of 2 engineers.}
\resumeItem{Executed GTM strategies using Reddit and referral programs, driving user acquisition without paid ads.}
\resumeItem{Ranked key features at \#3 in search results within 2 weeks using Ahrefs and SEO optimization.}
\resumeItem{Implemented PostHog analytics to track user journeys, inform feature prioritization, and optimize retention.}
\resumeItem{Maintained technical oversight, architecting a multi-cloud serverless AWS/Cloudflare backend with ~1\% infrastructure cost.}
\resumeItemListEnd


\resumeSubheading
{Backend and DevOps Engineer}{June 2021 -- December 2025}
{Syslify}{UK, Remote}
\resumeItemListStart
\resumeItem{Led backend and infrastructure development for multiple production systems, collaborating with stakeholders to translate business requirements into scalable technical solutions.}
\resumeItem{Built and maintained backends for two e-commerce platforms using TypeScript, Express, and MongoDB, supporting end-to-end data and user management.}
\resumeItem{Migrated legacy stacks to Terraform-based IaC, managing AWS, GCP, Cloudflare, and GitHub infrastructure with improved reliability and reproducibility.}
\resumeItem{Designed and implemented CI/CD pipelines using GitHub Actions, enabling automated testing, builds, and deployments across environments.}
\resumeItem{Reduced CI costs by ~90\% through self-hosted runners on AWS Fargate and optimized Docker layer caching strategies.}
\resumeItem{Implemented blue/green deployments and improved release workflows, increasing system stability and reducing downtime during production releases.}
\resumeItem{Improved security posture by implementing SSO (Microsoft Entra ID), strengthening RBAC, and enhancing secret management practices.}
\resumeItem{Optimized infrastructure usage by rightsizing EC2 and non-production environments, reducing costs by ~70\% while maintaining performance.}
\resumeItem{Managed and tuned OpenSearch clusters for production workloads, improving search performance and reliability.}
\resumeItemListEnd

\resumeSubheading
{Associate Software Engineer}{Nov 2023 -- Sept 2024}
{Vfairs}{Lahore, Remote, Part time}
\resumeItemListStart
\resumeItem{Configured and executed load tests simulating up to 10,000 concurrent users to ensure system stability.}
\resumeItem{Developed and optimized 40+ job scrapers, increasing data acquisition by 50\%.}
\resumeItemListEnd


\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Tashreeh.org} $|$ \emph{React, NextJs, Data Pipelines, OCR}}{}
\resumeItemListStart
\resumeItem{Led the end-to-end development of a web platform dedicated to reading and understanding Urdu poetry, taking full ownership of the product vision, UI/UX design, and core architecture.}
\resumeItem{Engineered a data pipeline using multiple models to process scanned Urdu literature books into a searchable SQL database.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Finasaan} $|$ \emph{NextJS, AI/ML, Web Scraping, Cloudflare}}{}
\resumeItemListStart
\resumeItem{Built a financial literacy platform for Pakistan with AI-powered guidance for investing, insurance, and tax filing, integrating real-time market data (KSE-100, mutual funds, gold prices).}
\resumeItem{Developed the full agentic chatbot independently and acquired 100+ waitlist signups through product validation and launch positioning.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{AWS WAF Manager} $|$ \emph{React, AWS, Bash, GitHub Actions}}{}
\resumeItemListStart
\resumeItem{Built an operational tool to manage banned IPs and monitor security rules in AWS WAF, streamlining a previously cumbersome workflow.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{National University of Science and Technology}{Islamabad, Pakistan}
{Bachelor of Science in Computer Science}{}
\resumeSubHeadingListEnd

\end{document}